### 2015-05-24 docs/report/array_merging.tex
Adds shared merge benchmark doc.

\subsection{Conclusion}
The benchmark shows that the best alternative to merge small \ttarray{}s into a larger one is using \code{TypedArray::Set} method.

>>>>

\subsection{\tstarray{} merge benchmark}

The benchmark presented modifies \ttarray{} merge benchmarks to support \tstarray{}s. The implementation removes \dataview{} test case as it is not supported by \tstarray{}:
\bmcode{http://jsperf.com/sharedtypedarray-merge}{../../spikes/2.4.1/sharedMerge.js}

The results for the benchmark are displayed in Figure~\ref{fig:shared-typed-array-merge}.
\img{Comparing \tstarray{} merge approaches}{../../spikes/2.4.1/sharedMerge}{fig:shared-typed-array-merge}

\subsection{Conclusion}
The benchmark shows that the best alternative to merge small arrays into a larger one is using \code{Set} method of eighter \ttarray or \tstarray.
